Importación de data
```{r}
library(rio)
link1="https://github.com/20175813/TRABAJO_ESTADISTICA/raw/master/Law%20mandates%20equal%20remuneration%20for%20females%20and%20males%20for%20work%20of%20equal%20value%20(1%3Dyes%3B%200%3Dno).xlsx"
equalRemuneration=import(link1)

link2="https://github.com/20175813/TRABAJO_ESTADISTICA/raw/master/The%20law%20prohibits%20discrimination%20in%20access%20to%20credit%20based%20on%20gender%20(1%3Dyes%3B%200%3Dno).xlsx"
credit=import(link2)

link3="https://github.com/20175813/TRABAJO_ESTADISTICA/raw/master/There%20is%20legislation%20on%20sexual%20harassment%20in%20employment%20(1%3Dyes%3B%200%3Dno).xlsx"
sexualHarassment=import(link3)

link4="https://github.com/20175813/TRABAJO_ESTADISTICA/raw/master/There%20is%20legislation%20specifically%20addressing%20domestic%20violence%20(1%3Dyes%3B%200%3Dno).xlsx"
domesticViolence=import(link4)

link5="https://github.com/20175813/TRABAJO_ESTADISTICA/raw/master/There%20is%20no%20legal%20provision%20that%20requires%20a%20married%20woman%20to%20obey%20her%20husband%20(1%3Dyes%3B%200%3Dno).xlsx"
obeyHusband=import(link5)

```

Limpieza de data equalRemuneration
Law mandates equal remuneration for females and males for work of equal value (1=yes; 0=no)
```{r}
names(equalRemuneration)
equalRemuneration[,c(1,2,4,5,6,7,8,9,10,11,12,13,14,15,16)]=NULL
names(equalRemuneration)=c("Pais", "equalRemuneration")
equalRemuneration=equalRemuneration[-c(264:268),]
equalRemuneration=equalRemuneration[-c(106:109),]
equalRemuneration=equalRemuneration[-c(61:64),]
equalRemuneration=equalRemuneration[-c(130:133),]
equalRemuneration=equalRemuneration[-c(99:100),]
equalRemuneration=equalRemuneration[-c(260, 252),]

str(equalRemuneration)
equalRemuneration$equalRemuneration = as.numeric(equalRemuneration$equalRemuneration)

equalRemuneration$Pais=trimws(equalRemuneration$Pais,whitespace = "[\\h\\v]")

write.csv(equalRemuneration, file = "equalRemuneration.csv", row.names = FALSE)
```

Limpieza de data credit
The law prohibits discrimination in access to credit based on gender (1=yes; 0=no)
```{r}
credit=credit[-c(1:263),]
credit=credit[-c(264:268),]
credit[,c(1,2,4,5,6,7,8,9,10,11,12,13,14,15,16)]=NULL

names(credit)=c("Pais", "credit")

str(credit)
credit$credit = as.numeric(credit$credit)

credit$Pais=trimws(credit$Pais,whitespace = "[\\h\\v]")

write.csv(credit, file = "credit.csv", row.names = FALSE)
```

Limpieza de data sexualHarrasment
There is legislation on sexual harassment in employment (1=yes; 0=no)
```{r}
sexualHarassment=sexualHarassment[-c(1:263, 527:1057),]
sexualHarassment[,c(1,2,4,5,6,7,8,9,10,11,12,13,14,15,16)]=NULL
names(sexualHarassment)=c("Pais", "sexualHarassment")

str(sexualHarassment)
sexualHarassment$sexualHarassment=as.numeric(sexualHarassment$sexualHarassment)

sexualHarassment$Pais=trimws(sexualHarassment$Pais,whitespace = "[\\h\\v]")

write.csv(sexualHarassment, file = "sexualHarassment.csv", row.names = FALSE)
```

Limpieza de data domesticViolence
There is legislation specifically addressing domestic violence (1=yes; 0=no)
```{r}
domesticViolence=domesticViolence[-c(1:526, 790:1057),]
domesticViolence[,c(1,2,4,5,6,7,8,9,10,11,12,13,14,15,16)]=NULL
names(domesticViolence)=c("Pais", "domesticViolence")

str(domesticViolence)
domesticViolence$domesticViolence=as.numeric(domesticViolence$domesticViolence)

domesticViolence$Pais=trimws(domesticViolence$Pais,whitespace = "[\\h\\v]")

write.csv(domesticViolence, file = "domesticViolence.csv", row.names = FALSE)
```

Limpieza de data obeyHusband
There is no legal provision that requires a married woman to obey her husband (1=yes; 0=no)
```{r}
obeyHusband=obeyHusband[-c(1:789, 1053:1057),]
obeyHusband[,c(1,2,4,5,6,7,8,9,10,11,12,13,14,15,16)]=NULL
names(obeyHusband)=c("Pais", "obeyHusband")

str(obeyHusband)
obeyHusband$obeyHusband = as.numeric(obeyHusband$obeyHusband)

obeyHusband$Pais=trimws(obeyHusband$Pais,whitespace = "[\\h\\v]")

write.csv(obeyHusband, file = "obeyHusband.csv", row.names = FALSE)
```

Formateo de tablas 
Merge1: Credit + domesticViolence
```{r}
datatotal<-merge(credit, domesticViolence, by="Pais")
```

Merge2: datatotal + equalRemuneration
```{r}
datatotal2<-merge(datatotal, equalRemuneration, by="Pais")
```

Merge3: datatotal2 + obeyHusband
```{r}
datatotal3<-merge(datatotal2, obeyHusband, by="Pais")
```

Merge4: barrLegCul = datatotal3 + sexualHarassment
```{r}
barLegCul<-merge(datatotal3, sexualHarassment, by="Pais")
```


Guardar data final 
```{r}
write.csv(barLegCul, file = "barLegCul.csv", row.names = FALSE)
```




